Between Subgraph Isomorphism and Maximum Common Subgraph

### 2016-09-13 paper/paper.tex
Just nuke the acks for now, for space
Switch to AAAI style
Page layout rejiggery

\usepackage[pass]{geometry}

\usepackage{ijcai16}
\usepackage{times}
\usepackage{complexity}
\usepackage{microtype}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{amsthm}
\usepackage{cleveref}
\usepackage{tikz}
\usepackage{mathtools}
\usepackage{graphicx}
\usepackage{multicol}
\usepackage[ruled,vlined]{algorithm2e}

@@

@@

\begin{figure}[t]
    \centering
    \begin{tikzpicture}[every node/.style={circle, inner sep=0.5mm}]
        \node[fill=black] (p) {};
        \node[fill=black] (b) [above of = p,node distance=10mm] {};
        \node[fill=black] (a) [left of = b] {};
        \node[fill=black] (c) [right of = b] {};
        \node[fill=black] (d) [above of = b,node distance=10mm] {};

@@

        \path (p) edge (a) edge (b) edge (c)
            (a) edge (d)
            (b) edge (c) edge (d)
            (c) edge (d);
        \end{tikzpicture}\hspace{0.5cm}\begin{tikzpicture}[every node/.style={circle, inner sep=0.5mm}]
        \node[fill=gray!50] (a1) [right of = d, node distance = 2cm] {};
        \node[fill=black] (b1) [right of = a1] {};
        \node[fill=gray!50] (c1) [right of = b1] {};
        \node[fill=black] (a2) [below of = a1] {};
        \node[fill=black] (b2) [right of = a2] {};
        \node[fill=black] (c2) [right of = b2] {};
        \node[fill=gray!50] (a3) [below of = a2] {};
        \node[fill=black] (b3) [right of = a3] {};
        \node[fill=gray!50] (c3) [right of = b3] {};

@@

        \path[color=gray!50] (a1) edge (b1) edge (a2)
            (b1) edge (c1)
            (c1) edge (c2)
            (a2) edge (b2) edge (a3)
            (c2) edge (c3)
            (a3) edge (b3)
            (b3) edge (c3);
        \path[line width=0.4mm] (b1) edge (a2) edge (b2) edge (c2)
            (a2) edge (b3)
            (b2) edge (c2) edge (b3)
            (c2) edge (b3);
    \end{tikzpicture}\hspace{0.5cm}\begin{tikzpicture}[every node/.style={circle, inner sep=0.5mm}]
        \node[fill=black] (p) {};
        \node[draw=none] (b) [above of = p,node distance=10mm] {};
        \node[fill=black] (a) [left of = b] {};
        \node[fill=black] (c) [right of = b] {};
        \node[fill=black] (d) [above of = b,node distance=10mm] {};

@@

% \begin{figure}
%     \begin{center}
%         \begin{tikzpicture}[every node/.style={circle, inner sep=1mm}]
%             \node[fill=black] (p) {};
%             \node[draw=none,right of = p,node distance=3mm,yshift=-1mm] {$p$};
%             \node[fill=uofglawn] (n2) [above of = p,node distance=12mm] {};
%             \node[fill=uofgpumpkin] (n1) [left of = n2] {};
%             \node[fill=uofglawn] (n3) [right of = n2] {};
%             \node[fill=uofgcobalt] (q) [above of = n2,node distance=12mm] {};
%             \path (p) edge (n1) edge (n2) edge (n3)
%                 (n1) edge (q)
%                 (n2) edge (n3) edge (q)
%                 (n3) edge (q);
%         \end{tikzpicture}
%         \caption{Example of neighbourhood degree filtering cases}
%         \label{fig:nds}
%     \end{center}
% \end{figure}

@@

\begin{figure}
    \centering
    \includegraphics*{gen-graph-ids.pdf}
    \caption{The amount of domain reduction achieved for the induced problem, with increasing values
    of $k$. The $y$ value shows for how many instances we may reduce the initial search space to be
    at most the $x$ proportion of the size the search space would be for the maximum common subgraph
    problem.}\label{figure:ids}
\end{figure}

@@

\begin{figure*}[tb]
    \centering
    \includegraphics*{gen-graph-constraints-induced-0.pdf}
    \includegraphics*{gen-graph-constraints-induced-1.pdf}
    \includegraphics*{gen-graph-constraints-induced-2.pdf}
    \includegraphics*{gen-graph-constraints-induced-3.pdf}
    \includegraphics*{gen-graph-constraints-induced-4.pdf}
    \includegraphics*{gen-graph-constraints-induced-5.pdf}

@@

\begin{figure*}[tb]
    \centering
    \includegraphics*{gen-graph-which-k-by-family.pdf}
    \caption{The proportion of instances, in different families, which become satisfiable for
    increasing values of $k$. The ``larger'' instances are those where we can prove unsatisfiability for
    $k = 5$, whilst the gap between the top of the bar and the top of the graph is the fraction of
    instances where a timeout was reached for at least one value of $k$.}\label{figure:which-k}
\end{figure*}

@@

\section*{Acknowledgements}

We'd like to thank some people whose names we've removed for anonymous review for providing us with
source code and problem instances, and someone at one of our institutions for inspiration.

\bibliographystyle{named}
\bibliography{paper}

>>>>

\setlength{\pdfpagewidth}{8.5in}
\setlength{\pdfpageheight}{11in}

\usepackage{aaai17}

\usepackage{times}
\usepackage{helvet}
\usepackage{courier}
\usepackage{complexity}
\usepackage{microtype}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{amsthm}
\usepackage{cleveref}
\usepackage{tikz}
\usepackage{mathtools}
\usepackage{graphicx}
\usepackage{multicol}
\usepackage[ruled,vlined]{algorithm2e}

@@

\setcounter{secnumdepth}{2}

@@

\begin{figure}[t]
    \centering
    \begin{tikzpicture}[every node/.style={circle, inner sep=0.5mm}]
        \node[fill=black] (p) {};
        \node[fill=black] (b) [above of = p,node distance=5mm] {};
        \node[fill=black] (a) [left of = b] {};
        \node[fill=black] (c) [right of = b] {};
        \node[fill=black] (d) [above of = b,node distance=5mm] {};

@@

        \path (p) edge (a) edge (b) edge (c)
            (a) edge (d)
            (b) edge (c) edge (d)
            (c) edge (d);
        \end{tikzpicture}\hspace{0.5cm}\begin{tikzpicture}[every node/.style={circle, inner sep=0.5mm}]
        \node[fill=gray!50] (a1) [right of = d, node distance = 2cm] {};
        \node[fill=black] (b1) [right of = a1] {};
        \node[fill=gray!50] (c1) [right of = b1] {};
        \node[fill=black] (a2) [below of = a1, node distance=6mm] {};
        \node[fill=black] (b2) [right of = a2] {};
        \node[fill=black] (c2) [right of = b2] {};
        \node[fill=gray!50] (a3) [below of = a2, node distance=6mm] {};
        \node[fill=black] (b3) [right of = a3] {};
        \node[fill=gray!50] (c3) [right of = b3] {};

@@

        \path[color=gray!50] (a1) edge (b1) edge (a2)
            (b1) edge (c1)
            (c1) edge (c2)
            (a2) edge (b2) edge (a3)
            (c2) edge (c3)
            (a3) edge (b3)
            (b3) edge (c3);
        \path[line width=0.4mm] (b1) edge (a2) edge (b2) edge (c2)
            (a2) edge (b3)
            (b2) edge (c2) edge (b3)
            (c2) edge (b3);
    \end{tikzpicture}\hspace{0.5cm}\begin{tikzpicture}[every node/.style={circle, inner sep=0.5mm}]
        \node[fill=black] (p) {};
        \node[draw=none] (b) [above of = p,node distance=5mm] {};
        \node[fill=black] (a) [left of = b] {};
        \node[fill=black] (c) [right of = b] {};
        \node[fill=black] (d) [above of = b,node distance=5mm] {};

@@

\begin{figure}
    \centering
    \includegraphics*{gen-graph-ids.pdf}
    \caption{The amount of domain reduction achieved for the induced problem, with increasing
    $k$. The $y$ value shows for how many instances we may reduce the initial search space to be
    at most the $x$ proportion of the size the search space would be for the maximum common subgraph
    problem.}\label{figure:ids}
\end{figure}

@@

\begin{figure*}[t]
    \centering
    \includegraphics*{gen-graph-constraints-induced-0.pdf}
    \includegraphics*{gen-graph-constraints-induced-1.pdf}
    \includegraphics*{gen-graph-constraints-induced-2.pdf}
    \includegraphics*{gen-graph-constraints-induced-3.pdf}
    \includegraphics*{gen-graph-constraints-induced-4.pdf}
    \includegraphics*{gen-graph-constraints-induced-5.pdf}

@@

@@

\begin{figure}[h!]
    \centering
    \includegraphics*{gen-graph-which-k-by-family.pdf}
    \caption{The proportion of instances, in different families, which become satisfiable for
    increasing values of $k$. The ``larger'' instances are those where we can prove unsatisfiability for
    $k = 5$, whilst the gap between the top of the bar and the top of the graph is the fraction of
    instances where a timeout was reached for at least one value of $k$.}\label{figure:which-k}
\end{figure}

@@

% \section*{Acknowledgements}

\bibliographystyle{aaai}
\bibliography{paper}
